Model-based pretreatment for regression with correlated variables.

### 2014-04-15 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@530 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@531 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Introduction}
%la régression et ses problèmes
Linear regression is a very standard and efficient method providing a predictive model with a good interpretability even  for non-statistician. Therefore, linear regression is used in nearly all the fields where statistics are made \cite{montgomery2012introduction}, from industry and astronomy \cite{isobe1990linear} to sociology \cite{longford2012revision}.
Linear regression is a very classic situation but sometimes it has to face an also classical problem: the variance of the estimators. We note the linear regression model:
\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon} \label{regressionsimple}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the  $n\times 1$ response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I}_n)$ the noise of the regression, with $\boldsymbol{I}_n$ the $n$-sized identity matrix and $\sigma_Y >0$. The $p\times 1$ vector $\boldsymbol{\beta}$ is the vector of the coefficients of the regression, that can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{OLS}). %As shown in section \ref{sectionOLS}, 
	Estimation of $\boldsymbol{\beta}$ requires the inversion of $\boldsymbol{X}'\boldsymbol{X}$ which will be ill-conditioned or even singular if some covariates depend linearly from each other. 
Conditionning of $\boldsymbol{X}'\boldsymbol{X}$ get worse based on two aspects : the dimension $p$ (number of covariates) of the model (the more covariates you have the greater variance you get)
	 and the correlations within the covariates: strongly correlated covariates give bad-conditioning and increase variance of the estimators .

	With the rise of informatics, datasets contain more and more covariates and thus dimension reduction becomes a necessity. Moreover, increasing the number of covariates also increases the chance to have correlated ones. It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favored to improve the process instead of only predict defects, so robust estimation is needed.
		~\\	~\\

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \lambda \textrm{ with } \lambda>0
	\end{equation}
	But Ridge regression do not aim at selecting covariates because coefficients tends to 0 but don't reach 0.
	So it gives difficult interpretations for large values of $p$.	
	Moreover, real datasets imply many irrelevant variables so we have to use variable selection methods.

>>>>

\section{Introduction}
%la régression et ses problèmes
Linear regression is a very standard and efficient method providing a predictive model with a good interpretability even  for non-statistician. Therefore, linear regression is used in nearly all the fields where statistics are made \cite{montgomery2012introduction}, from industry and astronomy \cite{isobe1990linear} to sociology \cite{longford2012revision}.
However, linear regression has to face the problem of the variance of the estimators.
%Linear regression is a very classic situation but sometimes it has to face an also classical problem: the variance of the estimators. 
We note the linear regression model:
\begin{equation}
		\boldsymbol{Y}_{|\boldsymbol{X}}=\boldsymbol{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon} \label{regressionsimple}
	\end{equation}
	where $\boldsymbol{X}$ is the $n\times p$ matrix of the explicative variables, $\boldsymbol{Y}$ the  $n\times 1$ response vector and $\boldsymbol{\varepsilon} \sim \mathcal{N}(\boldsymbol{0},\sigma_Y^2\boldsymbol{I}_n)$ the noise of the regression, with $\boldsymbol{I}_n$ the $n$-sized identity matrix and $\sigma_Y >0$. The $p\times 1$ vector $\boldsymbol{\beta}$ is the vector of the coefficients of the regression, that can be estimated by $\hat{\boldsymbol{\beta}}$ with Ordinary Least Squares (\textsc{OLS}). %As shown in section \ref{sectionOLS}, 
	Estimation of $\boldsymbol{\beta}$ requires the inversion of $\boldsymbol{X}'\boldsymbol{X}$ which will be ill-conditioned or even singular if some covariates depend linearly from each other. 
Conditionning of $\boldsymbol{X}'\boldsymbol{X}$ get worse based on two aspects : the dimension $p$ (number of covariates) of the model (the more covariates you have the greater variance you get)
	 and the correlations within the covariates: strongly correlated covariates give bad-conditioning and increase variance of the estimators .

	With the rise of informatics, datasets contain more and more covariates,% and thus dimension reduction becomes a necessity. Moreover, 
	increasing the chance to have correlated ones.  It will be illustrated with examples from steel industry in the last section of this paper (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). 
	 In such a context, variance of the estimators can lead to arbitrary results whereas interpretation and prediction are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favoured to improve the process instead of only predict defects, so robust estimation is needed.
		~\\	~\\

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \boldsymbol{\hat{\beta}}=\operatorname{argmin} \left\lbrace \parallel \boldsymbol{Y}-\boldsymbol{X\beta}\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel \boldsymbol{\beta} \parallel_2^2\leq \lambda \textrm{ with } \lambda>0
	\end{equation}
	But this penalty is not guided by the correlations. It is the same for each covariates and will be too large for independent covariates and/or too small for correlated ones. So the efficiency is of such a method is limited. 
	Moreover, coefficients tend to 0 but don't reach 0 so it gives difficult interpretations for large values of $p$. Real datasets often imply many irrelevant variables so variable selection would be favoured when possible.
